The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-05-23 manuscript/manuscript.tex
Update for the paper draft

The tight correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties (e.g. stellar mass \smass, luminosity \lhost) suggests an evolutionary connection. A powerful way to test this co-evolution hypothesis is to trace the correlations back in cosmic time. For this purpose, we obtained multi-band {\it Hubble Space Telescope} of  a sample of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ (look-back time 8-10 Gyrs). By applying state-of-the-art tools to the images we obtained accurate host galaxy luminosity and stellar mass. The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts. \textcolor{blue}{We enlarge the sample of the \mbh-\smass~and \mbh-\lhost~relations using previously published measurements and compare to the local to infer their evolution. We find the \mbh-\smass\ relation by our distant sample is inconsistent with the local \mbh-\smass$_{\rm, bluge}$ relation. We take selection effect into account to fit this offset as \mbh/\smass$\propto(1+z)^\gamma$, and obtain $\gamma = 0.80\pm0.30$. Considering that there is evidence showing our sample are composed of bulge and disk components, our result indicates BHs 8-10 Gyrs ago reside in bulges, if not entire galaxies, which contain lower \smass\ than today. Accounting for passive evolution, we find the \mbh-\lhost\ relation is also inconsistent with the local in a similar way. The evolution of both correlations is consistent with a scenario where the black hole grows first, followed by morphological transformations of host galaxies from late to early-types.}

@@

We focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$ \textcolor{blue}{(\mbh\ estimated using \halpha\ emission line).} We present the selection window that used to choose the sample in Figure~\ref{fig:selection}. We list all the AGN systems analyzed in this work in Table~\ref{tab:objlist}. Overall, our final sample is composed of 32 new observations by \hst/WFC3.

\begin{figure}
\centering
{
\includegraphics[height=0.4\textwidth]{fig/AGN_selection.pdf}
}
\caption{\label{fig:selection} 
\textcolor{red}{Figure to be updated} We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($L_{\rm Bol}/L_{\rm Edd}$) and \mbh. Our sample (color coded) falls well below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}. For comparing propose, we plot the high$-z$ luminous SDSS QSO samples from the reference \citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}. 
}
\end{figure}

@@

We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
For comparison with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11a) to define our zero-point. The sample by B10 consists of 19 \mbh-\lhost\ measured with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex). The work of B11 contains 25 \mbh-\smass\ local active AGNs, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex). To increase the local \smass\ and \mbh\ to the higher range, we also include 30 inactive galaxies (mainly ellipticals or S0) as measured by \citet{H+R04}. It is worth noting that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample. In other words, our local comparison is the \mbh-\smass$_{Bulge}$ and not those involving total quantities.

@@

%\textcolor{red}{Need to add the uncertainty level of their inference}.

@@

\subsection{\mbh-\lhost\ relation}\label{sec:ml}
We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}. Following common practice, we fit the local relation as a linear relation,
\begin{eqnarray}
\label{eq:MLlocal}
\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{L_R}{10^{10}L_{\odot}}),
\end {eqnarray}
which enables direct comparison to the distant sample. The figure shows that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones, indicating that the black hole mass and the host luminosity located at a similar relation at different galaxy age.

\begin{figure}
\centering
{\includegraphics[width=0.5\textwidth]{fig/MBH-L_obs.pdf}}
\caption{\label{fig:ML} 
Illustration of observed correlations between \mbh-\lhost, with local linear relation indicated. The redshift are color-coded, for distant and intermediate AGNs.
}
\end{figure}

However, considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame. Especially, in a passive evolution scenario, we expect \lhost\ to fade over time. 
We consider this scenario following \citet{Ding2017b} and parametrize the luminosity evolution with the functional form as
$d{\rm mag}_{\rm R} \sim d\log(1+z)$, i.e.,
\begin{eqnarray}
\label{eq:L_relation}
\log(L_{R,0})=\log(L_{R}) - 1.48 \log (1+z).
\end{eqnarray} 
This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$. We refer to \citet[][section 5.4]{Ding2017b} for more details and find that, after transferring the \lhost\ to today, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts. To quantitatively understand this trend, we fit the offset as a function of redshift in form as:
\begin{eqnarray}
\label{eq:offset}
\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
\end{eqnarray} 
where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{L_{R,0}}{10^{10}L_{\odot}})$. The best-fit and  1-$\sigma$ inference are $\gamma = 0.70 \pm 0.15$.

\textcolor{blue}{Of course, this is a simplified correction, as we only consider the evolution of the host galaxy but not the BH. Anyway, we couldn't exactly know how they were evolving to $z=0$. Analyzing the correlation of the \mbh-\smass\ would be more efficient to help directly understand the connection between their coevolution.}

%\begin{figure}
%\centering
%{
%\includegraphics[height=0.4\textwidth]{fig/MBH-L-vz.pdf}
%}
%\caption{\label{fig:ML-vz} 
%Illustration of the offset in log\mbh\ (VS. $L_R$) as a function of redshift. The orange band is the intrinsic scatter of local linear relation.}
%\end{figure}

%Given that the current result does not take into account selection effects yet, we will draw the conclusion in section~\ref{select_eff}.

\subsection{\mbh-\smass\ relation}\label{sec:mm}
In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample. We visually see that the relations for the three samples are close from one to another.

Similarly, we consider the local as linear relation to fit offset (i.e., $\Delta\log \mathcal M_{\rm BH}$) as a function of $\gamma \log (1 + z)$. We obtain the $\gamma  = 0.74 \pm 0.17$, i.e. tentative evidence for evolution, see Figure~\ref{fig:MM-vz}, panel (a). We also show the ratio of \mbh-\smass\ of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b). We highlight that our results are less biased in both the measurement of \mbh\ and \smass.

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style1.pdf}}&
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style0.pdf}}\\
\end{tabular}
\caption{\label{fig:MM-vz} 
Left: illustration of the offset in log\mbh\ (VS. \smass) as a function of redshift. Right: redshift evolution of the \mbh/\smass.  }
\end{figure*}

\textcolor{blue}{We also note that in Figure~\ref{fig:MM-vz}, panel (a), most of our new measurement is visually within the scatter of the local sample. The inference of the positive $\gamma$ seems to stem from the four outliers AGN systems which happens to have lower host mass relative to the BH mass. Thus, we only take the rest of the 28 sample and rerun the statistical analysis, aim to test if offset still exist among them only. As a result, we obtain the $\gamma  = 0.54 \pm 0.22$, indicating a slighter but still positive evolution.}

@@

We highlight that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses. That is, we are comparing the \mbh-\smass$_{,total}$ at the distant universe to the \mbh-\smass$_{,bulge}$ at the local. Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.

@@

\subsection{Selection effect}
\label{select_eff}
\textcolor{blue}{
Our AGN sample is selected based on the AGN luminosity and \halpha\ broad emission line, with lower nuclear-to-host ratios, which would introduce the bias in the inference of the evolution of the scaling relation if not properly taken into consideration~\citep{Tre++07, Bennert++2011, Schulze2014, Park15}, known as Malmquist bias. In theory, the simulation~\citep{DeG++15} also find the scaling relations by the selected samples have steeper feature than the random ones, highlighting the necessity of eliminating the selection biases. }

\textcolor{blue}{
We take selection effects into account using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}. Following \citet{Park15, Ding2017b}, we generate the simulating samples from a combination of the local active \mbh\ function by \cite{Schulze2010} and the local samples adopted in this work. We then added Gaussian random noise to the simulated samples as a function of two free parameters, $\gamma$ and \sint, where \sint\ is the intrinsic scatter when considering the scaling relation as linear. According to the observed distribution, we consider the observational selection of \mbh\ of our samples by lower and upper limits of $[7.7, 8.8]$ to model their distribution. To evaluate the posterior at the given $\gamma$ and \sint, for each object, we consider the likelihood of observing such object using the simulated sample, and consider whether the object would be selected or not, given the sensitivity. In addition, we adopt both uniform (flat) prior and lognormal prior for \sint\ (using the inference from linear fitting).
}

\textcolor{blue}{
Combining the 32 AGNs together with the intermediate redshift sample, we present the inferred  $\gamma$ and \sint\ in the two-dimensional planes in Figure~\ref{fig:select_effect}. Both the \mbh-\lhost\ and \mbh-\smass\ correlations have been considered. With a lognormal prior for \sint, the fitted $\gamma$ are $0.6\pm0.3$ (\mbh-\lhost) and $0.8\pm0.3$ (\mbh-\smass), consistent with the inference by the flat prior. These inference are consistent with the previous values (Section~\ref{sec:ml} and Section~\ref{sec:mm}) without considering the selection effect, indicating that the evolution feature of our sample exist globally in the overall samples. Furthermore, we find that the final inferred scatter \sint$\sim 0.3-0.5$ are similar to the local scatter, suggesting that the scatter of the scaling relation at high redshift are similar to local ones and indicating that we have not significantly underestimated/overestimated our errors for high redshift samples.
}

\textcolor{blue}{
We also study the selection effect by only consider the new 32 AGNs, result in a higher evolution trend with a higher value of $\gamma$. We show all the result of the $\gamma$ and \sint\ in the Table~\ref{table:gamma_sf}.
}

\begin{table}
\centering
    \caption{The summary for the different inference of $\gamma$.}\label{table:gamma_sf}
     \resizebox{8cm}{!}{
     \begin{tabular}{cccc}
     \hline
     Sample & Selection effects& \mbh-\lhost &  \mbh-\smass \\
     &&&\\
     \hline\hline
32 AGNs + intermediate & No & 0.70$\pm$0.15 & 0.74$\pm$0.17 \\
32 AGNs + intermediate& Yes & 0.60 $\pm$ 0.30 & 0.80 $\pm$ 0.30 \\
32 AGNs & No & 1.13$\pm$0.20 & 0.80$\pm$0.20\\
32 AGNs& Yes & 1.70$\pm$0.40 & 1.30$\pm$0.50\\
     \hline
     \end{tabular}}
    \tablecomments{
    Entire sample includes the 32 AGNs and the intermediate redshift AGNs from the reference in Section~\ref{sec:compare_sample}. Note that the adopted \lhost\ have been transferred to today assuming the passive evolution scenario using Equation~\ref{eq:L_relation}.
The results of selection effects used the lognormal prior of \sint.
}
\end{table}

\begin{figure*}
\centering
\begin{tabular}{c c}
\subfloat[\mbh-\lhost, flat prior]
{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_flatprior.pdf}}&
\subfloat[\mbh-\lhost, lognormal prior]
{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior.pdf}}\\
\subfloat[\mbh-\smass, flat prior]
{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_flatprior.pdf}}&
\subfloat[\mbh-\smass, lognormal prior]
{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_lognormprior.pdf}}\\
\end{tabular}
\caption{\label{fig:select_effect} 
Constraining the evolution factor $\gamma$ using Equation~\ref{eq:offset}, with intrinsic scatter \sint, using Monte Carlo simulation, by taking selection effects into account. The adopted sample includes 32 AGNs and the intermediate redshift AGNs. Upper panels: the $\gamma$ for the \mbh-\lhost\ relation, using flat prior of \sint panel-(a) and lognormal prior panel-(b). Bottom panel presents the result for \mbh-\smass\ relation.
}
\end{figure*}

\section{discussion}
\label{sec:dis}
\subsection{Systematic error}

\textcolor{blue}{
In this work, we use the start-of-the-art techniques to derive the host flux from the AGN image. The fidelity of the inferred apparent magnitudes of the host galaxies are high. Nevertheless, we adopt one stellar population to the overall sample to derive the rest-frame R band luminosity and stellar mass.
We note that adopting the private stellar populations for each samples which havs both multi-band host magnitude could be more robust in principle. However, considering that the host magnitude in ACS band is faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost. Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry.
We highlight that, in this particular paper, we focus most on the decomposing of the AGN image to present our inference of the host. In the mean time, we carry out a rapid analysis of the \mbh\ and host properties relations. The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.}

\textcolor{blue}{
At last, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates. That is to say, the intrinsic scatter is not necessarily worse at high-$z$ than the low-$z$.}

@@

Combining out high-$z$ measurements with the intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13}, we compared the scaling relations to the ones by the local with main results summarized as follows:
\begin{enumerate}
\item The \mbh-\smass\ relations at higher redshift are inconsistent with the local ones, i.e. Figure~\ref{fig:MM}, \ref{fig:MM-vz}.
\item Considering the correction for passive evolution of galaxy luminosity, the \mbh-\lhost\ relations at higher redshift are inconsistent with the local ones,  i.e. Figure~\ref{fig:ML}-(b), \ref{fig:ML-vz}.
\item The offsets of by the evolution are well described by the form $\Delta\log\mathcal M_{\rm BH}= \gamma \log (1 + z)$. Taking intro account selection effect, we obtain $\gamma = 0.8\pm0.3$ (\mbh-\smass) and $\gamma = 0.6\pm0.3$ (\mbh-\lhost).
\item We compare the properties of our active galaxy sample to the ones from inactive galaxy in the CANDLES imaging survey at the same redshift range, finding no significant discrepancy among them.
\end{enumerate}

@@

Looking into the future, the forthcoming lunching of {\it James Webb Space Telescope} ({\it JWST}) would provide the high quality imaging data of AGN at higher redshift (up to $z\sim$7-10) and thus trace the evolution of correlation at more distant universe. Furthermore, {\it JWST} is capable of showing the morphology of structures feeding black hole accretion and feedback on the host galaxy~\citep{Ford2014}, thus providing the opportunity to understand the origin of the scaling relations and their evolution.

>>>>

The tight correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties (e.g. stellar mass \smass, luminosity \lhost) suggests an evolutionary connection. A powerful way to test this co-evolution hypothesis is to trace the correlations back in cosmic time. For this purpose, we obtained multi-band {\it Hubble Space Telescope} of  a sample of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ (look-back time 8-10 Gyrs). By applying state-of-the-art tools to the images we obtained accurate host galaxy luminosity and stellar mass. The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts. \textcolor{blue}{We enlarge the sample using previously published measurements and compare to the local to infer their evolution. We find the \mbh-\smass\ relation by our distant sample is inconsistent with the local \mbh-\smass$_{\rm, bluge}$ relation. We take selection effect into account to fit this offset as \mbh/\smass$\propto(1+z)^\gamma$, and obtain $\gamma = 0.80\pm0.30$. Considering that there is evidence showing our sample are composed of bulge and disk components, our result indicates BHs 8-10 Gyrs ago reside in bulges, if not entire galaxies, which contain lower \smass\ than today. This indication also exist in the \mbh-\lhost\ relation, once account for the passive evolution of the host luminosity. The evolution of both correlations is consistent with a scenario where the black hole grows first, followed by morphological transformations of host galaxies from late to early-types.}

@@

We focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$ \textcolor{blue}{(BH mass estimated using \halpha\ emission line).} We present the selection window that used to choose the sample in Figure~\ref{fig:selection} and list all the AGN systems analyzed in this work in Table~\ref{tab:objlist}. Overall, our final sample is composed of 32 new observations by \hst/WFC3.

\begin{figure}
\centering
{
\includegraphics[height=0.4\textwidth]{fig/AGN_selection.pdf}
}
\caption{\label{fig:selection} 
\textcolor{red}{Figure needs to be updated.} We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($L_{\rm Bol}/L_{\rm Edd}$) and \mbh. Our sample (color coded) falls well below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}. For comparing propose, we plot the high$-z$ luminous SDSS QSO samples from the reference \citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}. 
}
\end{figure}

@@

We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
For comparison with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point. The sample by B10 consists of 19 \mbh-\lhost\ measured with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex). The work of B11 contains 25 \mbh-\smass\ local active AGNs, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex). To increase the local \smass\ and \mbh\ to the higher range, we also include 30 inactive galaxies (mainly ellipticals or S0) as measured by \citet{H+R04} (hereafter HR04).

It is worth noting that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample. In other words, our local comparison is the \mbh-\smass$_{Bulge}$ and not those involving total quantities.

@@

@@

\subsection{\mbh-\lhost\ relation}\label{sec:ml}
We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}. Following common practice, we fit the local relation as a linear relation,
\begin{eqnarray}
\label{eq:MLlocal}
\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{L_R}{10^{10}L_{\odot}}),
\end {eqnarray}
which enables direct comparison to the distant sample. The inferred local relations are presented in the Figure~\ref{fig:ML}, showing that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones. The observational result shows that the black hole mass and the host luminosity located at a similar relation at different galaxy age.

{\color{blue} 
Considering that both the black hole and host galaxy are expected to evolve over cosmic time, it is essential to transfer high-$z$ measurements to their values at today so as to compare them in an equivalent frame. We will present the discussion of this comparison in Section~\ref{sec:ml-ev}.

\begin{figure}
\centering
{\includegraphics[width=0.5\textwidth]{fig/MBH-L_obs.pdf}}
\caption{\label{fig:ML} 
Illustration of observed correlations between \mbh-\lhost, with local linear relation indicated. 
%The redshift are color-coded, for distant and intermediate AGNs.
The black line and the blue colored equation indicates the best-fit result of local sample as Equation~\ref{eq:MLlocal}, with $1-\sigma$ confidence interval colored as gray region.
}
\end{figure}

\subsection{\mbh-\smass\ relation}\label{sec:mm}
In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample. We visually see that the relations for the three samples are close from one to another. Similar as Equation~\ref{eq:MLlocal}, we consider the local \mbh-\smass\ relations as linear relation as:
\begin{eqnarray}
\label{eq:MMlocal}
\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}),
\end {eqnarray}

To understand the evolution for high$-z$ relations, we fit the offset as a function of redshift in form as:
\begin{eqnarray}
\label{eq:offset}
\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
\end{eqnarray} 
where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$. We obtain $\gamma  = 0.74 \pm 0.21$, i.e. tentative evidence for evolution, see Figure~\ref{fig:MM-vz}, panel (a). We also show the ratio of \mbh-\smass\ of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b).

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style1.pdf}}&
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style0.pdf}}\\
\end{tabular}
\caption{\label{fig:MM-vz} 
Left: illustration of the offset in log\mbh\ (VS. \smass) as a function of redshift. The orange band is the intrinsic scatter of local linear relation. Right: \mbh/\smass\ as a function of redshift.}
\end{figure*}

We also note that in Figure~\ref{fig:MM-vz}, panel (a), most of our new measurement is visually within the scatter of the local sample. The inference of the positive $\gamma$ seems to stem from the four outliers AGN systems which happens to have lower host mass relative to the BH mass. Thus, we only take the rest of the 28 sample and rerun the statistical analysis, aim to test if offset still exist among them only. As a result, we obtain the $\gamma  = 0.55 \pm 0.29$, indicating a slighter but still positive evolution, i.e. Figure~\ref{fig:MM_restsample}.

@@

It is worth note that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses. That is, we are comparing the \mbh-\smass$_{,total}$ at the distant universe to the \mbh-\smass$_{,bulge}$ at the local. Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.

@@

\subsection{Selection effect}
\label{select_eff}

Our AGN sample is manually selected based on the mass of BH, the Eddington rates, and \halpha\ broad emission line, with low nuclear-to-host ratios. When adopting the inference from the selected sample to the overall sample without properly considering the selection effect, bias could be introduced~\citep{Tre++07, Bennert++2011, Schulze2014, Park15}. In theory, the simulation~\citep{DeG++15} also find the scaling relations by the selected samples have steeper feature than the random ones, highlighting the necessity of eliminating the selection biases.

We take selection effects into account using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}. Following \citet{Park15, Ding2017b}, we generate the simulating samples from a combination of the local active \mbh\ function by \cite{Schulze2010} and the local samples adopted in this work. We then added Gaussian random noise to the simulated samples as a function of two free parameters, $\gamma$ and \sint, where \sint\ is the intrinsic scatter when considering the scaling relation as linear. According to the observed distribution, we consider the observational selection of \mbh\ of our samples by lower and upper limits of $[7.7, 8.8]$ to model their distribution. To evaluate the posterior at the given $\gamma$ and \sint, for each object, we consider the likelihood of observing such object using the simulated sample, and consider whether the object would be selected or not, given the sensitivity. In addition, we adopt both uniform (flat) prior and lognormal prior for \sint\ (using the inference from linear fitting).

Combining the 32 AGNs together with the intermediate redshift sample, we present the inferred  $\gamma$ and \sint\ in the two-dimensional planes in Figure~\ref{fig:select_effect}. With a lognormal prior for \sint, the fitted $\gamma = 0.8\pm0.3$, consistent with the inference by the flat prior. These inference are consistent with the previous values without considering the selection effect in Section~\ref{sec:mm}, indicating that the evolution feature of our sample exist globally in the overall samples. Furthermore, we find that the final inferred scatter \sint$\sim 0.3$ are similar to the local scatter, suggesting that the scatter of the scaling relation at high redshift are similar to local ones and indicating that we have not significantly underestimated/overestimated our errors for high redshift samples.

We also study the selection effect by only consider the new 32 AGNs, result in a higher evolution trend with a higher value of $\gamma$. We show all the result of the $\gamma$ and \sint\ in Table~\ref{table:gamma_sf}.

\begin{table}
\centering
    \caption{The summary for the different inference of $\gamma$.}\label{table:gamma_sf}
     \resizebox{8cm}{!}{
     \begin{tabular}{cccc}
     \hline
     Sample & Selection effects &  \mbh-\smass & \mbh-\lhost \\
     &&&\\
     \hline\hline
32 AGNs + intermediate & No & 0.74$\pm$0.21 & 0.70$\pm$0.18 \\
32 AGNs + intermediate& Yes & 0.80 $\pm$ 0.30 & 0.60 $\pm$ 0.30 \\
32 AGNs & No & 0.80$\pm$0.27  & 1.13$\pm$0.23\\
32 AGNs& Yes & 1.30$\pm$0.50 & 1.70$\pm$0.40 \\
     \hline
     \end{tabular}}
    \tablecomments{
    Entire sample includes the 32 AGNs and the intermediate redshift AGNs from the reference in Section~\ref{sec:compare_sample}. Note that the adopted \lhost\ have been transferred to today assuming the passive evolution scenario using Equation~\ref{eq:L_relation}.
The results of selection effects used the lognormal prior of \sint.
}
\end{table}

\begin{figure*}
\centering
\begin{tabular}{c c}
\subfloat[\mbh-\smass, flat prior]
{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_flatprior.pdf}}&
\subfloat[\mbh-\smass, lognormal prior]
{\includegraphics[width=0.5\textwidth]{fig/MM_MC_seleff_lognormprior.pdf}}\\
\end{tabular}
\caption{\label{fig:select_effect} 
Constraining the evolution factor $\gamma$ of \mbh-\smass\ relation using Equation~\ref{eq:offset}, with intrinsic scatter \sint, using Monte Carlo simulation, by taking selection effects into account. The adopted sample includes 32 AGNs and the intermediate redshift AGNs, using flat prior of \sint\ (left panel) and lognormal prior (right panel).
}
\end{figure*}

\section{discussion}
\label{sec:dis}

\subsection{Host luminosity passive evolution correction}\label{sec:ml-ev}
In a passive evolution scenario, we expect \lhost\ to fade over time. We transfer the \lhost\ for distant samples at today and compare them to the local in an equivalent frame

We consider this scenario following \citet{Ding2017b} and parametrize the luminosity evolution with the functional form as
$d{\rm mag}_{\rm R} \sim d\log(1+z)$, i.e.,
\begin{eqnarray}
\label{eq:L_relation}
\log(L_{R,0})=\log(L_{R}) - 1.48 \log (1+z).
\end{eqnarray} 
This formalism is more accurate to fit a broad range redshift comparing to a single slope as $d$mag$/dz$. We refer to \citet[][section 5.4]{Ding2017b} for more details.

We find that, as showing in Figure~\ref{fig:ML-vz}-(a), after transferring the \lhost\ to today, at fixed \mbh, the BH in the more distant universe tends to reside in less luminous hosts, which is consistent to the \mbh-\smass\ relation. To quantitatively understand this trend, we fit the offset as a function of redshift in form following Equation~\ref{eq:offset}. The best-fit and 1-$\sigma$ inference are $\gamma = 0.71 \pm 0.18$, i.e.  Figure~\ref{fig:ML-vz}-(b). We consider the selection effect use the same approach as introduced in Section~\ref{select_eff}, and obtain $\gamma = 0.6\pm0.3$ with lognormal prior, showing in Figure~\ref{fig:ML-vz}-(c), (d).

This section is based on a simplified correction, after all we are not clear exactly how they were evolving to $z=0$. Also, we only consider the evolution of the host galaxy but not the BH. Thus, the correlation of the \mbh-\smass\ would be more efficient to understand the co-evolution connection between BH and its host galaxy.

\begin{figure*}
\centering
\begin{tabular}{c c}
\subfloat[\mbh-\lhost\ relation, evolution-corrected]
{\includegraphics[height=0.4\textwidth]{fig/MBH-L_ev.pdf}}&
\subfloat[offset in log\mbh\ (VS. \lhost) as a function of redshift]
{\includegraphics[height=0.4\textwidth]{fig/MBH-L-vz.pdf}}\\
\subfloat[\mbh-\lhost, flat prior]
{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_flatprior.pdf}}&
\subfloat[\mbh-\lhost, lognormal prior]
{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior.pdf}}\\
\end{tabular}
\caption{\label{fig:ML-vz} 
Same as previous figures but for \mbh-\lhost relation, considering the passive evolution correction for host galaxy luminosity.}
\end{figure*}

\subsection{Systematic error}
In this work, we use the start-of-the-art techniques to derive the host flux from the AGN image. The fidelity of the inferred apparent magnitudes of the host galaxies are high. Nevertheless, we adopt one stellar population to the overall sample to derive the rest-frame R band luminosity and stellar mass.
We note that adopting the private stellar populations for each samples which havs both multi-band host magnitude could be more robust in principle. However, considering that the host magnitude in ACS band is faint (host-total flux ratio $< 30\%$), the fidelity of the SED fitting is actually lost. Perhaps the best way to derive the stellar population is to combining our measurements to the ground-based photometry.
We highlight that, in this particular paper, we focus most on the decomposing of the AGN image to present our inference of the host. In the mean time, we carry out a rapid analysis of the \mbh\ and host properties relations. The measurements incorporating the ground-based photometry and the comparison with the simulations are presented in our companion paper.

At last, we stress that the uncertainty in the scaling relations is dominated by the single epoch black hole mass estimates. That is to say, the intrinsic scatter is not necessarily worse at high-$z$ than the low-$z$.

\subsection{Affect using different local anchor}
%Why we local anchor for this paper, for a consistency to the previous work.
%However, the other local samples could be different.
%The comparison of the local MM?
%The corresponding systemic error?
To determining the scaling relations at the local universe, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04}. This adopting enable a direct comparison with the previous work \citep{Park15, SS13}, which adopted the same local sample. We realize that in the literature, there are other local measurements which could shift the local anchor hence affect the conclusion of the co-evolution. For example, we compare our local \mbh-\smass\ sample to the ones by \citet{Kormendy13} (hereafter K13), as showing in Figure~\ref{fig:local_MM_comp}.

We compare the inference of the local linear relation using different combinations of the local sample. It turn out that the inference by HR04+B11 has a lower intercept value to the sample by K13+B11 by 0.3~dex. Apparently, adopting the local by K13+B11 would raise the local relation, hence mitigate the offset of $\Delta\log\mathcal M_{\rm BH}$ and $\gamma$ by a factor of 0.3~dex. Given the values in Table~\ref{fig:MM_restsample}, this mitigating wouldn't affect our inference of $\gamma$ from positive to negative, however, the current offset highlights the importance to build a solid local baseline for the future studies (Bennert et al., in prep).

\begin{figure}
\centering
{\includegraphics[width=0.5\textwidth]{fig/local_MM_comparison.pdf}}
\caption{\label{fig:local_MM_comp} 
The local \mbh-\smass\ relations from different literature. The black and red line are the best-fit linear relation using the sample by combining B11+HR04 and B11+ K13, respectively, showing a 0.3~dex offset in the intercept value.
}
\end{figure}

@@

Combining out high-$z$ measurements with the intermediate redshift samples from the literature~\citep{Park15, Bennert11, SS13}, we compared the scaling relations to the ones by the local with main results summarized as follows:
\begin{enumerate}
\item The \mbh-\smass\ relations at higher redshift are inconsistent with the local ones, i.e. Figure~\ref{fig:MM}, \ref{fig:MM-vz}.
\item Considering the correction for passive evolution of galaxy luminosity, the \mbh-\lhost\ relations at higher redshift are inconsistent with the local ones,  i.e. Figure~\ref{fig:ML-vz}.
\item The offsets of by the evolution are well described by the form $\Delta\log\mathcal M_{\rm BH}= \gamma \log (1 + z)$. Taking intro account selection effect, we obtain $\gamma = 0.8\pm0.3$ (\mbh-\smass) and $\gamma = 0.6\pm0.3$ (\mbh-\lhost).
\item We compare the properties of our active galaxy sample to the ones from inactive galaxy in the CANDLES imaging survey at the same redshift range, finding no significant discrepancy among them.
\end{enumerate}

@@

Looking into the future, the forthcoming lunching of {\it James Webb Space Telescope} ({\it JWST}) would provide the high quality imaging data of AGN at higher redshift (up to $z\sim$7-10) and thus trace the evolution of correlation at more distant universe. Furthermore, {\it JWST} is capable of showing the morphology of structures feeding black hole accretion and feedback on the host galaxy~\citep{Ford2014}, thus providing the opportunity to understand the origin of the scaling relations and their evolution.
}
